---
title: "Cleaning"
author: "Grant Foster"
date: "2024-10-04"
output: html_document
---

```{r}
options(java.parameters = "-Xmx20g") #Java Heap Space Limits for Maxent
library(rJava)
library(tidyverse)
library(GIFT)
library(terra)
library(dismo)
library(predicts)
library(picante)
library(ape)
library(phytools)
library(stringr)
```


# Querying interaction data

Frugivory networks from Moulatlet 2023
```{r, eval=F}
Moulatlet <- read.csv(file="../Data/datalong_v08_06_2023_CLEANED.csv") #Read in moulet interaction data
Moulatletval <- Moulatlet %>% dplyr::select(., Scientific, plant_id, interaction, lat, lon) %>% #Filter down to unique interactions
  dplyr::filter(interaction %in% (c(0,1))) %>%  
  dplyr::select(., Scientific, plant_id, interaction, lat, lon) %>% 
  dplyr::rename(., Latitude=lat, Longitude=lon, Frugivore_Species=Scientific, Plant_Species=plant_id) %>%
  unique()

Moulatletval$interaction <- as.numeric(Moulatletval$interaction) #Make sure col is numeric

Moulatletval %>% 
  dplyr::group_by(., Frugivore_Species, Plant_Species, Latitude, Longitude) %>%
  dplyr::summarise(interaction=max(interaction, na.rm=T)) #If species have been observed both with a 0 and 1 at the same site, set to 1 (indicating we've seen this interaction here at least once)



Mcounts <- Moulatletval %>% dplyr::mutate(., speciesPair=paste(Frugivore_Species, Plant_Species, sep="-")) %>% #Make a "Species-pair" col
  group_by(., speciesPair) %>% #group by this
  dplyr::summarise(., pos=sum(interaction), tot=n(), neg=tot-pos) #count the number of positive and negative interaction presences across the Moulatletval data

Mcounts$prop <- Mcounts$pos/Mcounts$tot  #Calculate the total prevalence of interactions across all coocurences


#pdf(file="Figures/MoulatletInterSummary.pdf")
Mcounts %>% dplyr::filter(., tot>9) %>%
ggplot(., aes(x=tot, y=prop))+geom_point(position = "jitter")+theme_classic()+ylab("Proportion of Interactions given Coocurence")+xlab("Number of Coocurrences")+ annotate("text", x = 31, y = .25, label = "211 interactions total")+ annotate("text", x = 31, y = .2, label = "44 birds, 37 plants")
#dev.off()


usable <- Mcounts %>% dplyr::filter(., tot>4 & prop>0) %>% unique()#Number of interactions with at least 5 records, and interact at at least 1 site. 

Moulatletval <- Moulatletval %>% dplyr::mutate(., speciesPair=paste(Frugivore_Species, Plant_Species, sep="-")) #Create Species-pair column

usable <- left_join(usable, Moulatletval, by="speciesPair") %>% unique() #Grab the usable interactions w/lat-long data
```


```{r, eval=F}
length(unique(usable$Frugivore_Species))
length(unique(usable$Plant_Species))

library(rnaturalearth)
library(rnaturalearthdata)

world <- ne_countries(scale = "medium", returnclass = "sf")
usable$Latitude <- as.numeric(usable$Latitude)
usable$Longitude <- as.numeric(usable$Longitude)

#pdf(file="Figures/MoulatletMap_10occ.pdf", width=11, height=8.5)
ggplot(data = world) +
    geom_sf()+theme_classic()+geom_point(data=usable, aes(x=Longitude, y=Latitude))
#dev.off()
```

Plant-Pollinator networks queried from Web of Life

Querying the web of life API. 
Tutorial for how to do this found here: https://www.web-of-life.es/tutorial/session-download-data.html
```{r}
# define the base url
base_url <- "https://www.web-of-life.es/"   
json_url2 <- paste0(base_url,"get_networks.php?interaction_type=Pollination") 

WolPols <- jsonlite::fromJSON(json_url2)
WolMeta <- read.csv(paste0(base_url,"get_network_info.php")) %>%dplyr::filter(., network_type%in%"Pollination")
#length(unique(WolPols$network_name)) # 174 Networks
```

Downloading the metaData on Wol data so that we have geometries
```{r, eval=F}
WolMeta <- read.csv(paste0(base_url,"get_network_info.php"))
WolMeta <- WolMeta %>% dplyr::filter(., network_type%in%"Pollination") #Make sure we have only pollination
length(unique(WolMeta$network_name)) #174 networks
WolMeta <- WolMeta %>% dplyr::select(., network_name, region, latitude, longitude) %>% left_join(WolPols, ., by="network_name")
```

```{r, eval=F}
WolMeta <- WolMeta %>% 
  group_by(latitude, longitude) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup() #Some networks are grouped across time but are at the same site-I'm adding a grouping column for those here. 

Wolsumm <- dplyr::select(WolMeta, ID, longitude, latitude, species1, species2) %>% unique() %>%#Grab uniques
  dplyr::rename(., Plant_Species=species1, Pollinator_Species=species2)
Wolsumm$interaction<- 1 #All these were observed in the WOL data

#Below we add all of the unobserved but potential interactions at each site (Ex. If a plant and a pollinator are both recorded in a site but don't have a recorded interaction, this adds that as a row with a "0" in the interaction columns)
exPoll <- NULL
nsites <- length(unique(Wolsumm$ID)) #Look across each sites
for(i in 1:nsites){
  temp <- dplyr::filter(Wolsumm, ID==unique(Wolsumm$ID)[i]) #Grab the recorded interaction
  nms_temp <- expand(temp, Pollinator_Species, Plant_Species) #Expand to all possible interactions
  nms_temp <- left_join(nms_temp, temp, by=c("Pollinator_Species", "Plant_Species")) #Grab the true interactions
  nms_temp$interaction[is.na(nms_temp$interaction)==TRUE] <- 0 #The NAs left are unobserved at this site
  nms_temp$latitude <- rep(temp$latitude[1], nrow(nms_temp)) #Grab the correct spatial info + NetID
  nms_temp$longitude <- rep(temp$longitude[1], nrow(nms_temp))
  nms_temp$ID <- rep(temp$ID[1], nrow(nms_temp))
  exPoll <- rbind(exPoll, nms_temp) #save to my output object
}
```

Repeat the process from above to find the usuable sets of plant-pollinator interactions. 

```{r, eval=F}
pol2 <- dplyr::mutate(exPoll, speciesPair=paste(Pollinator_Species, Plant_Species, sep="-")) #Make a "Species-pair" col

pol2 <- pol2 %>% dplyr::group_by(., speciesPair, longitude, latitude) %>% dplyr::mutate(., interaction=max(interaction)) #In case there are repeated sites with 0 and 1 interactions, take the 1 (meaning it was observed there at least once)

pol2 <- dplyr::select(pol2, -ID) %>% unique() #remove any redundant sites

pol2 <- group_by(pol2, speciesPair) %>% #group by this
  dplyr::mutate(., pos=sum(interaction), tot=n(), neg=tot-pos)#count the number of positive and negative interaction presences across the pollinator data

pol2$prop <- pol2$pos/pol2$tot #create a proportion column

usable_Pol <-pol2 %>% dplyr::filter(., tot>4 & prop>0) %>% unique() #Filter to those that cooccur at at least 4 sites

usable_Pol <- dplyr::filter(usable_Pol, grepl(" sp\\d+", speciesPair)==F) #remove entries not ID'ed to species
```



```{r, eval=F}
WolMeta$speciesPair <- paste(WolMeta$species2, WolMeta$species1, sep="-")

WolUsable <- left_join(usable_Pol, WolMeta, by="speciesPair")
length(unique(WolUsable$species1))
length(unique(WolUsable$species2))
```
Below we create a df called "dat" which contains all the interactions that fit our criterion across both network types. 
```{r, eval=F}
colnames(usable)
usable2 <- dplyr::rename(usable, Animal_Species=Frugivore_Species) %>% dplyr::select(., "speciesPair", "Animal_Species", "Plant_Species", "interaction", "pos","neg","tot","prop","Longitude","Latitude")
usable2$Class <- "Frug"

usable_Pol2 <- usable_Pol %>% dplyr::rename(., Animal_Species=Pollinator_Species, Longitude=longitude, Latitude=latitude) %>% dplyr::select(., "speciesPair", "Animal_Species", "Plant_Species", "interaction", "pos","neg","tot","prop","Longitude","Latitude")
usable_Pol2$Class <- "Poll"

dat <- rbind(usable2, usable_Pol2)

#write.csv(dat, file="data/interactionOccs.csv", row.names = F)
#save(WolMeta, Moulatletval, file="data/interactionWebs.RDA")
```


Loading in the outputs created from above
```{r}
dat <- read.csv(file="data/interactionOccs.csv")
load(file="data/interactionWebs.RDA")
```


```{r}
frug1 <- dplyr::filter(dat, Class=="Frug")
poll1 <- dplyr::filter(dat, Class=="Poll")

hist(frug1$tot, main="Frugivore Interactions # of coccurences", xlab="# of coocs")
hist(poll1$tot, main="Pollinator Interactions # of coccurences", xlab="# of coocs")
```


Grabbing taxonkeys from rgbif to more easily interface with gbifdb
```{r}
taxa <- rgbif::name_backbone_checklist(unique(c(dat$Animal_Species, dat$Plant_Species)))
#Searched term is in verbatim_name column
taxa_safe <- dplyr::filter(taxa, is.na(speciesKey)==F)
#write.csv(taxa_safe, file="backbone_matches.csv", row.names=FALSE) #We use this output in GBIFdb_Querying.R to grab occurence points
```

# Quantifying interaction specialism
```{r}
FrugPartners <- dplyr::filter(Moulatletval, Frugivore_Species %in% dat$Animal_Species) #All interactions with the focal frugivore species
PollPartners <- dplyr::filter(WolPols, species2 %in% dat$Animal_Species) #All interactions with the focal pollinator species

trait_vector <- c("leaf area", "maximum fruit length", "maximum whole plant height", "maximum whole plant longevity", "minimum fruit length", "plant fruiting duration", "seed length", "seed mass", "whole plant height")

plants <- unique(FrugPartners$Plant_Species, WolPols$species1)
plants <- plants[grepl("\\d", plants)==FALSE]
#save(plants, file="BIENstuff.Rda")
```

Basis specificity (# of interactions)
```{r}
FrugSpecificity <- FrugPartners %>% dplyr::filter(., interaction==1) %>%
  dplyr::group_by(Frugivore_Species) %>%
  dplyr::summarise(nInteractions=length(unique(Plant_Species)))

PollSpecificity <- PollPartners %>%
  dplyr::group_by(species2) %>%
  dplyr::summarise(nInteractions=length(unique(species1)))
```

## Looking at Plant Traits (Floral Visitor Specialism)

Query those plants in BIEN
```{r}
#plant_traits <- BIEN::BIEN_trait_species(species=plants) #I had trouble running this all at once, so I split the query into 4 files of ~1k-1.5K each  
#write.csv(plant_traits, file="data/traits/plant_traits5K.csv", row.names = F)
BIENSP <- BIEN::BIEN_list_all()

pmatches <- plants[plants %in% BIENSP$species]
```
Loading in those plant traits and taking species-level averages

```{r}
dat1 <- read.csv(file="data/traits/plant_traits1K.csv")
dat2 <- read.csv(file="data/traits/plant_traits2K.csv")
dat34 <- read.csv(file="data/traits/plant_traits3-4K.csv")
dat5 <- read.csv(file="data/traits/plant_traits5K.csv")

ptraits <- rbind(dat1, dat2, dat34, dat5)
rm(dat1, dat2, dat34, dat5)

psums <- ptraits %>% group_by(., scrubbed_species_binomial, trait_name) %>%  dplyr::summarise(trait_mean=mean(trait_value, na.rm = TRUE))

ptrats_quant <- ptraits %>% dplyr::filter(., is.na(unit)==FALSE)
ptrats_quant$trait_value <- as.numeric(ptrats_quant$trait_value)

ptrats_quant <- dplyr::filter(ptrats_quant, trait_name!="diameter at breast height (1.3 m)" | project_pi !="Richard Condit") #This source has a bunch of dbh junk data; removing it.


ptrats_qual <- ptraits %>% dplyr::filter(., is.na(unit)==TRUE)

ptraitsum <- ptrats_quant %>% group_by(., scrubbed_species_binomial, trait_name) %>%  dplyr::summarise(trait_mean=mean(trait_value, na.rm = TRUE)) %>% dplyr::filter(., trait_mean>0)
```

Let's pivot these traits wider and see which ones we have a bunch of estimates of.
```{r}
wide <- pivot_wider(ptraitsum, id_cols=scrubbed_species_binomial, names_from=trait_name, values_from=trait_mean) #Pivot_wider

#filling in plant height. For species that don't have a "whole plant height" sub with max plant height
wide$`whole plant height`[is.na(wide$`maximum whole plant height`)==F& is.na(wide$`whole plant height`)==T] <- wide$`maximum whole plant height`[is.na(wide$`maximum whole plant height`)==F& is.na(wide$`whole plant height`)==T]

wide$`whole plant height`[is.na(wide$`minimum whole plant height`)== F& is.na(wide$`whole plant height`)==T] <- wide$`maximum whole plant height`[is.na(wide$`maximum whole plant height`)==F& is.na(wide$`whole plant height`)==T]

#Summarising how many species we have trait values for
sort(nrow(wide)-colSums(is.na(wide)), decreasing=T)

wide$fruitlength <- (wide$`maximum fruit length`-wide$`minimum fruit length`)/2 #If contains both min and max take mean
wide$fruitlength[is.na(wide$fruitlength)==T] <- wide$`maximum fruit length`[is.na(wide$fruitlength)==T] #If no mean, take max
wide$fruitlength[is.na(wide$fruitlength)==T] <- wide$`minimum fruit length`[is.na(wide$fruitlength)==T] #If no max, take min
BIENsum <- dplyr::select(wide, "scrubbed_species_binomial", "leaf area per leaf dry mass", "seed length", "seed mass", "whole plant height", "fruitlength", "diameter at breast height (1.3 m)") %>% unique()
hist(BIENsum$`diameter at breast height (1.3 m)`)
colnames(BIENsum) <- c("AccSpeciesName", "SLA_mm2/mg", "seed_length_mm", "seed_mass_mg", "plant_height_m", "fruit_length_mm", "DBH_cm")
```


Alright, now working with qualitative traits from BIEN
```{r}
ptrats_qual <- dplyr::filter(ptrats_qual, trait_name %in% c("flower color"))

flower_color_map_db2 <- c(
  # White
  "White" = "white",
  "White_" = "white",
  "Cream" = "white",
  "Creamy_white" = "white",
  "Cream-whitish" = "white",
  "White-cream" = "white",

  # Yellow
  "Yellow" = "yellow",
  "Yellowish" = "yellow",
  "Yellow-cream" = "yellow",
  "Cream-yellow" = "yellow",
  "White-golden_yellow" = "yellow",
  "Greenish_yellow" = "yellow",
  "Whitish-yellowish" = "yellow",

  # Green
  "Green" = "green",
  "Greenish" = "green",
  "Light_green" = "green",
  "Pale_green" = "green",
  "Green_buds" = "green",
  "Yellowish_green" = "green",
  "Yellow_green" = "green",
  "Whitish_green" = "green",
  "Light_green-whitish" = "green",
  "Pale_green-white" = "green",
  "White-green" = "green",
  "Green-whitish" = "green",
  "White-greenish" = "green",
  "Green-pale_green-cream"="green",

  # Red
  "Red" = "red",
  "Reddish" = "red",

  # Pink
  "Pink" = "pink",
  "White-pink" = "pink",

  # Orange
  "Orange" = "orange",

  # Blue
  "Blue" = "blue",

  # Brown
  "Brown" = "brown",
  "Browish" = "brown",
  "Yellowish_brown" = "brown",

  # Purple
  "Purple" = "purple",
  "Blue-purple" = "purple",
  "Purple-reddish" = "purple",
  "Pink-Light_purple" = "purple",

  # Multicolored
  "Green-golden_yellow" = "multicolored"
)
```

```{r}
ptrats_qual$FlowerColor_simple <- unname(
  flower_color_map_db2[ptrats_qual$trait_value]
)
ptrats_qual <- dplyr::select(ptrats_qual, scrubbed_species_binomial, FlowerColor_simple) %>% unique()

BIEN_flclr <- dplyr::select(ptrats_qual, scrubbed_species_binomial, FlowerColor_simple) %>% 
  unique() %>%
  mutate(value = 1) %>% #to grab positive for pivot_wider
    pivot_wider(
    names_from = FlowerColor_simple,
    values_from = value,
    values_fill = 0,
    names_prefix = "flower_"
) %>%
  dplyr::rename(., AccSpeciesName=scrubbed_species_binomial)
```

```{r}
BIENsum <- full_join(BIENsum, BIEN_flclr, by=join_by(AccSpeciesName))
```

Below is code starting to query GIFT, though I haven't actually incorporated it. 
GIFT First
```{r, eval=FALSE}
trait_meta <- GIFT_traits_meta()
GIFT_query <- dplyr::filter(trait_meta, Trait2 %in% c("Plant_height_mean", "DBH_min", "DBH_max", "Lifespan", "Seed_length_mean", "Fruit_length_mean", "Flower_colour", "SLA_mean"))

GIFT_Traits <- GIFT_traits(
  trait_IDs = GIFT_query$Lvl3,
  agreement = 0.66,
  bias_ref = TRUE,
  bias_deriv = TRUE,
  api = "https://gift.uni-goettingen.de/api/extended/",
  GIFT_version = "latest"
)
GIFT_query$

GIFT_Traits <- dplyr::filter(GIFT_Traits, work_species %in% plants)
```

Below I load in a TRY data request. 
https://www.try-db.org/TryWeb/Home.php
```{r, eval=FALSE}
library(rtry)
TRY <- rtry_import("data/TRYQuery_InterMod.txt")
TRY <- rtry::rtry_remove_dup(TRY)
TRY <- dplyr::filter(TRY, is.na(TraitID)==FALSE) #If missing, really mostly a random collection of measurements.

contTRY <- dplyr::filter(TRY, TraitID %in% c(26, 3106, 3117, 27, 918, 18))

contTRYsummary <- contTRY %>%
  dplyr::filter(., is.na(UnitName)==F) %>%
  dplyr::group_by(TraitName, TraitID, AccSpeciesName, UnitName) %>% 
  dplyr::summarise(., meanMeasure=mean(StdValue, na.rm=T), nmeasures=n())

qualTry <- dplyr::filter(TRY, TraitID %in%  c(59,207,585))
#write.csv(contTRYsummary, file="contTRYsummary.csv", row.names = F)
#write.csv(qualTry, file="qualTry.csv", row.names = F)
```

Loading in our intermediates
```{r}
contTRYsummary <- read.csv(file="contTRYsummary.csv")
qualTry <- read.csv(file="qualTry.csv")
```

Parsing Flower Color Strings
```{r}
fwrClr <- dplyr::filter(qualTry, TraitID==207)
fwrClr <- dplyr::filter(fwrClr, OrigValueStr %in% names(table(fwrClr$OrigValueStr)[table(fwrClr$OrigValueStr)>5])) #Keep only colors with at least 5 records (minimizing my string manipulation when I can)

fwrClr <- dplyr::filter(fwrClr, OrigValueStr != "/" ) #Slash

#Colormap initially created with help of chatgpt, but spotchecked with google translate to ensure accurate translations
flower_color_map_simple <- c(
  # Blue
  "blue" = "blue",
  "Blue" = "blue",
  "blau" = "blue",
  "dunkelblau" = "blue",
  "hellblau" = "blue",
  "hellblau, Schlund gelb" = "multicolored",

  # Brown
  "brown" = "brown",
  "Brown" = "brown",
  "bräunlich" = "brown",

  # Yellow
  "yellow" = "yellow",
  "Yellow" = "yellow",
  "gelb" = "yellow",
  "gelblich" = "yellow",
  "hellgelb" = "yellow",
  "goldgelb" = "yellow",
  "grünlichgelb" = "yellow",
  "blassgelb" = "yellow",
  "sattgelb" = "yellow",
  "schwefelgelb" = "yellow",
  "zitronengelb" = "yellow",
  "goldgelb, glänzend" = "yellow",
  "amarillo" = "yellow",

  # Green
  "green" = "green",
  "Green" = "green",
  "grün" = "green",
  "hellgrün" = "green",
  "grünlich" = "green",
  "gelblichgrün" = "green",
  "gelb, grün" = "green",
  "gelbgrün" = "green",
  "green, yellow" = "green",
  "verde" = "green",

  # Orange
  "orange" = "orange",
  "Orange" = "orange",

  # Purple, including violet terms
  "purple" = "purple",
  "Purple" = "purple",
  "purpurn" = "purple",
  "hellpurpurn" = "purple",
  "morado" = "purple",
  "violet" = "purple",
  "violett" = "purple",
  "hellviolett" = "purple",
  "lila" = "purple",
  "blauviolett" = "purple",
  "rotviolett" = "purple",

  # Red
  "red" = "red",
  "Red" = "red",
  "rot" = "red",
  "purpurrot" = "red",
  "rosenrot" = "red",
  "rosarot" = "red",
  "rojo" = "red",

  # Pink
  "pink" = "pink",
  "rosa" = "pink",
  "hellrosa" = "pink",
  "blassrosa" = "pink",
  "blass rosa" = "pink",
  "lebhaft rosa" = "pink",
  "rosado" = "pink",
  "rosa bis weiß" = "pink",
  "blass rosa bis fast weiß" = "pink",
  "weiß bis blassrosa" = "pink",
  "weiß bis hellrosa" = "pink",
  "weiß oder rosa" = "pink",
  "weiß bis rosa" = "pink",
  "weiß bis blass rosa" = "pink",

  # White
  "white" = "white",
  "White" = "white",
  "weiß" = "white",
  "weißlich" = "white",
  "grünlichweiß" = "white",
  "rötlichweiß" = "white",
  "gelblichweiß" = "white",
  "blanco" = "white",

  # Remaining compounds simplified to multicolored
  "weiß und gelb" = "multicolored",
  "weiß, am Grund gelb" = "multicolored",
  "weiß oder rötlich" = "multicolored",
  "pink, purple" = "multicolored",

  # Non-color / variable categories
  "various colors" = "variable",
  "sin flor" = "no_flower"
)

fwrClr$FlowerColor_simple <- unname(
  flower_color_map_simple[fwrClr$OrigValueStr] #map our flower color strings to our simplified mapping
)

fwrClr_Final <- dplyr::select(fwrClr, AccSpeciesName, FlowerColor_simple) %>% 
  unique() %>%
  mutate(value = 1) %>% #to grab positive for pivot_wider
    pivot_wider(
    names_from = FlowerColor_simple,
    values_from = value,
    values_fill = 0,
    names_prefix = "flower_"
)
```

Parsing Fruit/Seed Color Strings
```{r}
fruitClr <- dplyr::filter(qualTry, TraitID==585)
fruitClr <- dplyr::filter(fruitClr, OrigValueStr %in% names(table(fruitClr$OrigValueStr)[table(fruitClr$OrigValueStr)>5])) #Keep only colors with at least 5 records (minimizing my string manipulation when I can)

#again, colormap initially created with help of chatgpt, but spotchecked with google translate to ensure accurate translations
fruit_seed_color_map <- c(
  # Black
  "Black" = "black",
  "black" = "black",

  # Blue
  "Blue" = "blue",

  # Brown
  "Brown" = "brown",
  "brown" = "brown",
  "brownish" = "brown",
  "dark brown" = "brown",
  "pale brown" = "brown",
  "reddish brown" = "brown",
  "yellowish brown" = "brown",

  # Green
  "Green" = "green",
  "green" = "green",
  "greenish" = "green",
  "dark green" = "green",
  "green?" = "green",
  "yellowish green" = "green",

  # Orange
  "Orange" = "orange",
  "orange" = "orange",
  "orange-red" = "orange",
  "orange-brown" = "orange",

  # Pink
  "pink" = "pink",

  # Purple
  "Purple" = "purple",
  "purple" = "purple",

  # Red
  "Red" = "red",
  "red" = "red",
  "reddish" = "red",
  "bright red" = "red",
  "dark red" = "red",
  "young fruits pale almost white; turning bright red at maturity; and then brown with age" = "red",


  # White
  "White" = "white",
  "white" = "white",
  "whitish" = "white",
  "ivory" = "white",
  "white / cream" = "white",
  "beige" = "white",

  # Yellow
  "Yellow" = "yellow",
  "yellow" = "yellow",
  "yellowish" = "yellow",
  "straw-coloured" = "yellow",

  # Multicolored or variable
  "brown; black" = "multicolored",
  "yellow to orange" = "multicolored",
  "yellow; orange" = "multicolored",
  "orange; red" = "multicolored",
  "red; orange" = "multicolored",
  "orange to red" = "multicolored",
  "yellow; orange; red" = "multicolored",
  "red; black" = "multicolored",
  "yellow; red" = "multicolored",
  "green; red" = "multicolored",
  "pink; red" = "multicolored",
  "green; black" = "multicolored",
  "green; brown" = "multicolored",
  "white; red" = "multicolored",
  "red; brown" = "multicolored",
  "yellow; brown" = "multicolored",
  "orange; yellow" = "multicolored",
  "orange or red" = "multicolored",
  "purple-black" = "multicolored",
  "purple; black" = "multicolored",
  "black; purple" = "multicolored",
  "brown; yellow" = "multicolored",
  "orange; brown" = "multicolored",
  "green to red" = "multicolored",
  "purplish-black" = "multicolored",
  "black-purple" = "multicolored",
  "blue; black" = "multicolored",
  "brown to black" = "multicolored",
  "purple / black" = "multicolored",
  "brown/red" = "multicolored"
)

fruitClr$FruitSeedColor_simple <- unname(
  fruit_seed_color_map[fruitClr$OrigValueStr]
)

fruitClr <- fruitClr %>% #Collect species that have multiple entries for each color option
  dplyr::group_by(AccSpeciesName, FruitSeedColor_simple) %>%
  dplyr::summarise(Nvotes=n()) %>% 
  ungroup()

fruitClr_final <- fruitClr %>%
  group_by(AccSpeciesName) %>%
  arrange(desc(Nvotes), .by_group = TRUE) %>% #ORder by votes to take slice of most voted
  slice(1) 
```

Parsing lifespan estimates
```{r}
plantAge <- dplyr::filter(qualTry, TraitID==59)

#Again, making use of ChatGPT to create a string mapping function
map_lifespan <- function(x) {
  original <- x
  x <- trimws(tolower(as.character(x)))

  # Normalize obvious punctuation/spacing
  x <- gsub("\\s+", " ", x)
  x <- gsub("–|—", "-", x)

  out <- rep(NA_character_, length(x))

  # Empty / unknown-ish values
  out[is.na(original) | x == "" |
        x %in% c("unknown", "always questionable", "nope", "no", "yes")] <- "unknown"

  # Explicit non-perennial coded in as annuals (assumption)
  out[is.na(out) & x %in% c("not perennial", "perennial or not")] <- "annual"

  # Abbreviations and clear annuals
  annual_pat <- paste(
    c(
      "\\bannual\\b", "\\bannuals\\b",
      "\\bsummer annual\\b", "\\bsummer annuals\\b",
      "\\bwinter annual\\b", "\\bwinter annuals\\b",
      "\\bannuel\\b", "\\banual\\b", "\\bann\\b",
      "\\bsa\\b", "\\bwa\\b",
      "\\bephemeral\\b"
    ),
    collapse = "|"
  )

  # Clear biennials and misspellings
  biennial_pat <- paste(
    c(
      "\\bbiennial\\b", "\\bbiennials\\b",
      "\\bbiannual\\b", "\\bbisannual\\b", "\\bbiasannual\\b",
      "\\bbennial\\b", "\\bbieenial\\b", "\\bbiennual\\b",
      "\\bbi-annuals\\b"
    ),
    collapse = "|"
  )

  # Perennial terms and misspellings
  perennial_pat <- paste(
    c(
      "\\bperennial\\b", "\\bperennials\\b",
      "\\bpere\\b", "\\bper\\b", "\\bpereenial\\b", "\\bpernnial\\b",
      "\\bperennil\\b", "\\bwoody\\b", "\\btree\\b", "\\bshrub\\b",
      "\\bgeophytes\\b", "\\bhemicryptophytes\\b",
      "\\bperennial rootstock\\b",
      "\\bpluriennial\\b", "\\bpoly-annuals\\b",
      "\\bpolycarpic perennial\\b", "\\bmonocarpic perennial\\b",
      "\\bevergreen\\b"
    ),
    collapse = "|"
  )

  # Textual perennial duration classes
  out[is.na(out) & grepl("short-lived|short lived|shortperennial|short perennial|short-lived pp", x)] <- "perennial_lt5"
  out[is.na(out) & grepl("medium-lived|medium lived|moderate", x)] <- "perennial_5_50"
  out[is.na(out) & grepl("long-lived|long lived|\\blong\\b", x)] <- "perennial_50_plus"

  # Explicit poly-annual categories
  out[is.na(out) & grepl("poly-annuals.*5-50|5-50 years", x)] <- "perennial_5_50"
  out[is.na(out) & grepl("poly-annuals.*50 years|50 years.*long-lived", x)] <- "perennial_50_plus"
  out[is.na(out) & grepl("poly-annuals.*5 years|5 years.*short-lived", x)] <- "perennial_5_50"

  # If mixed annual/biennial/perennial, shortest option wins.
  # Annual has priority over biennial and perennial.
  out[is.na(out) & grepl(annual_pat, x)] <- "annual"

  # Biennial has priority over perennial, but only after annual has been checked.
  out[is.na(out) & grepl(biennial_pat, x)] <- "biennial"

  # Perennial-only text with no lifespan info
  out[is.na(out) & grepl(perennial_pat, x)] <- "perennial_unspecified"

  # Explicit inequality rules before generic numeric parsing
  out[is.na(out) & grepl("^>\\s*1\\s*years?$", x)] <- "perennial_unspecified"
  out[is.na(out) & grepl("^>\\s*2\\s*years?$", x)] <- "perennial_lt5"
  out[is.na(out) & grepl("^<\\s*5\\s*years?$", x)] <- "perennial_lt5"
  out[is.na(out) & grepl(">\\s*50\\s*years?", x)] <- "perennial_50_plus"
    out[is.na(out) & grepl("<\\s*5\\s*years?", x) & grepl("perennial|poly-annuals", x)] <- "perennial_lt5"
  
  # Numeric parser.
  # Rule:
  #   1 year or less -> annual
  #   >1 to <=2 years -> biennial
  #   >2 to <5 years -> perennial_lt5
  #   >=5 to <50 years -> perennial_5_50
  #   >=50 years -> perennial_50_plus
  #
  # For ranges or multiple values, use the minimum number, following your shorter-option rule.
  needs_numeric <- is.na(out)

  extract_min_number <- function(s) {
    nums <- regmatches(s, gregexpr("\\d+\\.?\\d*", s))[[1]]
    nums <- suppressWarnings(as.numeric(nums))
    nums <- nums[!is.na(nums)]
    if (length(nums) == 0) return(NA_real_)
    min(nums)
  }

  min_years <- rep(NA_real_, length(x))
  min_years[needs_numeric] <- vapply(x[needs_numeric], extract_min_number, numeric(1))

  out[is.na(out) & !is.na(min_years) & min_years <= 1] <- "annual"
  out[is.na(out) & !is.na(min_years) & min_years > 1 & min_years <= 2] <- "biennial"
  out[is.na(out) & !is.na(min_years) & min_years > 2 & min_years < 5] <- "perennial_lt5"
  out[is.na(out) & !is.na(min_years) & min_years >= 5 & min_years < 50] <- "perennial_5_50"
  out[is.na(out) & !is.na(min_years) & min_years >= 50] <- "perennial_50_plus"

  # Anything still unmapped
  out[is.na(out)] <- "unknown"

  out
}

plantAge$LifeSpan_simple <- map_lifespan(plantAge$OrigValueStr) #apply our mapping function to our plantAge dataset
```

```{r}
plantAge <- plantAge %>%
  dplyr::group_by(AccSpeciesName, LifeSpan_simple) %>%
  dplyr::summarise(Nvotes=n()) %>% 
  ungroup()

plantAge <- dplyr::filter(plantAge, LifeSpan_simple != "unknown") #remove unkowns

#In the case of a tie, we assign heirarchy to our lifespan options, choosing shortest available
lifespan_order <- c(
  "annual",
  "biennial",
  "perennial_lt5",
  "perennial_5_50",
  "perennial_50_plus",
  "perennial_unspecified"
)

plantAge_final <- plantAge %>%
  mutate(
    LifeSpan_rank = match(LifeSpan_simple, lifespan_order)
  ) %>%
  group_by(AccSpeciesName) %>%
  arrange(desc(Nvotes), LifeSpan_rank, .by_group = TRUE) %>% #First order by votes, then lifespan rank
  slice(1) %>% #Take the first entry after our arrange
  ungroup() %>%
  dplyr::select(AccSpeciesName, LifeSpan_simple, Nvotes)
```

Putting the TryData in one place
```{r}
qualTry_summary <- plantAge_final %>% dplyr::select(., -Nvotes) %>%
  full_join(., dplyr::select(fruitClr_final, -Nvotes), by = join_by(AccSpeciesName)) %>% #join fruit color
  full_join(., fwrClr_Final, by= join_by(AccSpeciesName)) #join flower color

traitname_map <- c("Fruit length"="fruit_length_mm",
  "Leaf area per leaf dry mass (specific leaf area, SLA or 1/LMA): undefined if petiole is in- or excluded"="SLA_mm2/mg",
  "Plant height"="plant_height_m",
  "Plant height vegetative"="plant_height_vegetative_m",
  "Seed dry mass"="seed_mass_mg",
  "Seed length"="seed_length_mm")

contTRYsummary <- dplyr::filter(contTRYsummary, is.na(meanMeasure)==F) %>%
  dplyr::filter(., is.na(TraitName)==F) 

contTRYsummary$TraitName <- unname(
  traitname_map[contTRYsummary$TraitName] #msimplify column names before pivoting
)

contTRYsummary <- contTRYsummary %>% 
  dplyr::select(., AccSpeciesName, TraitName, meanMeasure) %>%
  pivot_wider(., id_cols=AccSpeciesName, names_from=TraitName, values_from = meanMeasure)

Trysummary <- full_join(qualTry_summary, contTRYsummary, by=join_by(AccSpeciesName))
```

Combining our data into one trait set
```{r}
bien_cols <- setdiff(names(BIENsum), "AccSpeciesName")
try_cols  <- setdiff(names(Trysummary), "AccSpeciesName")

shared_cols <- intersect(bien_cols, try_cols)
bien_only   <- setdiff(bien_cols, shared_cols)
try_only    <- setdiff(try_cols, shared_cols)

PTraits <- full_join(
  BIENsum,
  Trysummary,
  by = "AccSpeciesName",
  suffix = c("_BIEN", "_TRY")
)

for (col in shared_cols) {
  PTraits[[col]] <- coalesce(
    PTraits[[paste0(col, "_BIEN")]],
    PTraits[[paste0(col, "_TRY")]]
  )
}

PTraits <- PTraits %>%
  dplyr::select(
    AccSpeciesName,
    all_of(shared_cols),
    all_of(bien_only),
    all_of(try_only)
  )
```


```{r}
focal <- c(unique(dat$Animal_Species), unique(dat$Plant_Species))
```

Determining Phylogenetic specificity of animal pollinators/dispersers

START HERE: ADDING POLYTOMIES
Fruiting Plants
```{r}
FrugPartners$Plant_Species[FrugPartners$Plant_Species=="Garcinia king\xe4ensis"] <- "Garcinia kingaensis"

FrugPartners$Plant_Species
FrugPartners$genera <- word(FrugPartners$Plant_Species, 1, 1)
FrugPartners$sp <- word(FrugPartners$Plant_Species, 2, 2)

BIEN_tree <- BIEN::BIEN_phylogeny_complete(n_phylogenies = 1, seed=1, replicates = 10)


FrugPlants <- FrugPartners %>%
  filter(!str_detect(sp, "\\d")) %>% 
  dplyr::select(., Plant_Species, genera, sp) %>% 
  unique()

#hist(node.depth.edgelength(BIEN_tree)[seq_len(Ntip(BIEN_tree))]) #Tree is ultrametric, but just doesn't seem due to rounding errors. 
#BIEN_tree <- force.ultrametric(BIEN_tree) #My big tree is too big to apply this to

#table(tolower(unique(FrugPlants$genera)) %in% BIEN_genera) #Out of 828 genera in our dataset, 503 have a congeneric match in the BIEN tree.
BIEN_plantkeep <- data.frame(tip=BIEN_tree$tip.label)
BIEN_plantkeep$genera <- BIEN_plantkeep$tip %>% 
  gsub("_"," ",.) %>%
  word(., 1,1) %>%
  tolower()

BIEN_plantkeep <- dplyr::filter(BIEN_plantkeep, genera %in% tolower(unique(FrugPlants$genera))) #Filtering out all species without congenerics in our frugivore dataset

FrugPlant_tree <- ape::keep.tip(BIEN_tree, BIEN_plantkeep$tip)
#FrugPlant_tree <- force.ultrametric(FrugPlant_tree)
```

Flowering Plants
```{r}
PollPartners <- PollPartners %>% dplyr::rename(.,"Plant_Species"=species1, "visitor"=species2)
PollPartners$genera <- word(PollPartners$Plant_Species, 1, 1) %>% tolower()
BIEN_plantkeep <- data.frame(tip=BIEN_tree$tip.label)
BIEN_plantkeep$genera <- BIEN_plantkeep$tip %>% 
  gsub("_"," ",.) %>%
  word(., 1,1) %>%
  tolower()

BIEN_plantkeep <- dplyr::filter(BIEN_plantkeep, genera %in% tolower(unique(PollPartners$genera))) #Filtering out all species without congenerics in our frugivore dataset
PollPlant_tree <- ape::keep.tip(BIEN_tree, BIEN_plantkeep$tip)
#save(FrugPlant_tree, PollPlant_tree, file="nonRoundedTrees.RDA")
```

```{r}
load(file="Ult_trees.RDA")
```



```{r}
dmatrix <- stats::cophenetic(Frug_treeUlt) 
dmatrix <- dmatrix/max(dmatrix) 

#String manipulation so tree tip names match
dat$plant_Tips <- gsub(pattern=" ", replace="_", x=dat$Plant_Species) 
#Only include plant species for which phylogenetic info is available
dat_phylo <- dplyr::filter(dat, plant_Tips %in% BIEN_subtree$tip.label) 

comm <- as.data.frame.matrix(table(dat_phylo$Frugivore_Species, dat_phylo$plant_Tips))#Binary, unweighted intraction matrix.
#The main function. Randomly swap tip labels 999 times and see whether the observed sets of plant interactors for each species is more phylogenetically clustered than this assumed distribution
frugivore_mpd <- picante::ses.mpd(comm, dmatrix, null.model = "independentswap", abundance.weighted=FALSE, runs = 999, iterations = 1000) 
```
```






## Looking at Animal Traits (Plant Specialism)
This is something we can revisit down the line if we want, but we're somewhat data limited right now. For now, we'll focus on plant traits, as the active choice of who to interact with is being made by the animal anyways, so specialism-generalism seems bit more relevant from that side. 
Pollinator Traits
Frugivore Traits (AvoNet)

# Creating SDMS
  Next steps + thoughts: perform PCA on smaller extent. Also do on icebox, or just do a subset. 
First, let's work on our climate data features. 
```{r}

```






```{r}
library(terra)

# Training presence coordinates
train_pres_xy <- Occurrences[id.training, c("Long", "Lat")]

# Training pseudo-absence/background coordinates
train_abs_xy <- Occurrences[id.training, c("Long_Psuedo", "Lat_Psuedo")]

# Convert to spatial vectors
train_pres_pts <- terra::vect(
  train_pres_xy,
  geom = c("Long", "Lat"),
  crs = terra::crs(Maxent.0)
)

train_abs_pts <- terra::vect(
  train_abs_xy,
  geom = c("Long_Psuedo", "Lat_Psuedo"),
  crs = terra::crs(Maxent.0)
)

pdf(file="Bannanaquit_Example.pdf", width=11, height = 8.5)
# Plot suitability
plot(Maxent.0, main = "MaxEnt suitability with training points")

# Add pseudo-absence/background points first
terra::points(
  train_abs_pts,
  pch = 1,
  col = "gray",
  cex = 0.6,
  alpha=0.6
)

# Add presence points on top
terra::points(
  train_pres_pts,
  pch = 16,
  col = "red",
  cex = 0.7,
  alpha=0.5
)

legend(
  "topright",
  legend = c("Training presence", "Training pseudo-absence"),
  pch = c(16, 1),
  col = c("red", "gray"),
  bty = "n",
  bg = "white"
)
dev.off()


pdf(file="Bannanaquit_blank.pdf", width=11, height = 8.5)
# Plot suitability
plot(Maxent.0)
dev.off()
```

Perform a PCA on our environmental data to grab some predictors
```{r}
Clima <- geodata::worldclim_global("worldclim", var="bio", res=2.5)
vals <- as.data.frame(Clima, na.rm = TRUE)
pca <- prcomp(vals, center = TRUE, scale = TRUE)

Clima_pca <- terra::predict(
  Clima,
  pca,
  index = 1:4,
  filename = "Clima_PCA_1to4.tif",
  overwrite = TRUE
)

PCA <- terra::rast("worldclim/Clima_PCA_1to8.tif")
```


```{r}

```


