---
title: "Cleaning"
author: "Grant Foster"
date: "2024-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(GIFT)
library(terra)
```


# Querying interaction data

Frugivory networks from Moulatlet 2023
```{r, eval=F}
Moulatlet <- read.csv(file="../Data/datalong_v08_06_2023_CLEANED.csv") #Read in moulet interaction data
Moulatletval <- Moulatlet %>% dplyr::select(., Scientific, plant_id, interaction, lat, lon) %>% #Filter down to unique interactions
  dplyr::filter(interaction %in% (c(0,1))) %>%  
  dplyr::select(., Scientific, plant_id, interaction, lat, lon) %>% 
  dplyr::rename(., Latitude=lat, Longitude=lon, Frugivore_Species=Scientific, Plant_Species=plant_id) %>%
  unique()

Moulatletval$interaction <- as.numeric(Moulatletval$interaction) #Make sure col is numeric

Moulatletval %>% 
  dplyr::group_by(., Frugivore_Species, Plant_Species, Latitude, Longitude) %>%
  dplyr::summarise(interaction=max(interaction, na.rm=T)) #If species have been observed both with a 0 and 1 at the same site, set to 1 (indicating we've seen this interaction here at least once)



Mcounts <- Moulatletval %>% dplyr::mutate(., speciesPair=paste(Frugivore_Species, Plant_Species, sep="-")) %>% #Make a "Species-pair" col
  group_by(., speciesPair) %>% #group by this
  dplyr::summarise(., pos=sum(interaction), tot=n(), neg=tot-pos) #count the number of positive and negative interaction presences across the Moulatletval data

Mcounts$prop <- Mcounts$pos/Mcounts$tot  #Calculate the total prevalence of interactions across all coocurences


#pdf(file="Figures/MoulatletInterSummary.pdf")
Mcounts %>% dplyr::filter(., tot>9) %>%
ggplot(., aes(x=tot, y=prop))+geom_point(position = "jitter")+theme_classic()+ylab("Proportion of Interactions given Coocurence")+xlab("Number of Coocurrences")+ annotate("text", x = 31, y = .25, label = "211 interactions total")+ annotate("text", x = 31, y = .2, label = "44 birds, 37 plants")
#dev.off()


usable <- Mcounts %>% dplyr::filter(., tot>4 & prop>0) %>% unique()#Number of interactions with at least 5 records, and interact at at least 1 site. 

Moulatletval <- Moulatletval %>% dplyr::mutate(., speciesPair=paste(Frugivore_Species, Plant_Species, sep="-")) #Create Species-pair column

usable <- left_join(usable, Moulatletval, by="speciesPair") %>% unique() #Grab the usable interactions w/lat-long data
```


```{r, eval=F}
length(unique(usable$Frugivore_Species))
length(unique(usable$Plant_Species))

library(rnaturalearth)
library(rnaturalearthdata)

world <- ne_countries(scale = "medium", returnclass = "sf")
usable$Latitude <- as.numeric(usable$Latitude)
usable$Longitude <- as.numeric(usable$Longitude)

#pdf(file="Figures/MoulatletMap_10occ.pdf", width=11, height=8.5)
ggplot(data = world) +
    geom_sf()+theme_classic()+geom_point(data=usable, aes(x=Longitude, y=Latitude))
#dev.off()
```

Plant-Pollinator networks queried from Web of Life

Querying the web of life API. 
Tutorial for how to do this found here: https://www.web-of-life.es/tutorial/session-download-data.html
```{r, eval=F}
# define the base url
base_url <- "https://www.web-of-life.es/"   
json_url2 <- paste0(base_url,"get_networks.php?interaction_type=Pollination") 

WolPols <- jsonlite::fromJSON(json_url2)
WolMeta <- read.csv(paste0(base_url,"get_network_info.php")) %>%dplyr::filter(., network_type%in%"Pollination")
length(unique(WolPols$network_name)) # 174 Networks
```

Downloading the metaData on Wol data so that we have geometries
```{r, eval=F}
WolMeta <- read.csv(paste0(base_url,"get_network_info.php"))
WolMeta <- WolMeta %>% dplyr::filter(., network_type%in%"Pollination") #Make sure we have only pollination
length(unique(WolMeta$network_name)) #174 networks
WolMeta <- WolMeta %>% dplyr::select(., network_name, region, latitude, longitude) %>% left_join(WolPols, ., by="network_name")
```

```{r, eval=F}
WolMeta <- WolMeta %>% 
    mutate(ID = group_indices(WolMeta, .dots=c("latitude", "longitude"))) #Some networks are grouped across time but are at the same site-I'm adding a grouping column for those here. 

Wolsumm <- dplyr::select(WolMeta, ID, longitude, latitude, species1, species2) %>% unique() %>%#Grab uniques
  dplyr::rename(., Plant_Species=species1, Pollinator_Species=species2)
Wolsumm$interaction<- 1 #All these were observed in the WOL data

#Below we add all of the unobserved but potential interactions at each site (Ex. If a plant and a pollinator are both recorded in a site but don't have a recorded interaction, this adds that as a row with a "0" in the interaction columns)
exPoll <- NULL
nsites <- length(unique(Wolsumm$ID)) #Look across each sites
for(i in 1:nsites){
  temp <- dplyr::filter(Wolsumm, ID==unique(Wolsumm$ID)[i]) #Grab the recorded interaction
  nms_temp <- expand(temp, Pollinator_Species, Plant_Species) #Expand to all possible interactions
  nms_temp <- left_join(nms_temp, temp, by=c("Pollinator_Species", "Plant_Species")) #Grab the true interactions
  nms_temp$interaction[is.na(nms_temp$interaction)==TRUE] <- 0 #The NAs left are unobserved at this site
  nms_temp$latitude <- rep(temp$latitude[1], nrow(nms_temp)) #Grab the correct spatial info + NetID
  nms_temp$longitude <- rep(temp$longitude[1], nrow(nms_temp))
  nms_temp$ID <- rep(temp$ID[1], nrow(nms_temp))
  exPoll <- rbind(exPoll, nms_temp) #save to my output object
}
```

Repeat the process from above to find the usuable sets of plant-pollinator interactions. 

```{r, eval=F}
pol2 <- dplyr::mutate(exPoll, speciesPair=paste(Pollinator_Species, Plant_Species, sep="-")) #Make a "Species-pair" col

pol2 <- pol2 %>% dplyr::group_by(., speciesPair, longitude, latitude) %>% dplyr::mutate(., interaction=max(interaction)) #In case there are repeated sites with 0 and 1 interactions, take the 1 (meaning it was observed there at least once)

pol2 <- dplyr::select(pol2, -ID) %>% unique() #remove any redundant sites


pol2 <- group_by(pol2, speciesPair) %>% #group by this
  dplyr::mutate(., pos=sum(interaction), tot=n(), neg=tot-pos)#count the number of positive and negative interaction presences across the Moulatletval data

pol2$prop <- pol2$pos/pol2$tot #create a proportion column

usable_Pol <-pol2 %>% dplyr::filter(., tot>4 & prop>0) %>% unique() #Filter to those that cooccur at at least 4 sites

usable_Pol <- dplyr::filter(usable_Pol, grepl(" sp\\d+", speciesPair)==F) #remove entries not ID'ed to species
```



```{r, eval=F}
WolMeta$speciesPair <- paste(WolMeta$species2, WolMeta$species1, sep="-")

WolUsable <- left_join(usable_Pol, WolMeta, by="speciesPair")
length(unique(WolUsable$species1))
length(unique(WolUsable$species2))
```
Below we create a df called "dat" which contains all the interactions that fit our criterion across both network types. 
```{r, eval=F}
colnames(usable)
usable2 <- dplyr::rename(usable, Animal_Species=Frugivore_Species) %>% dplyr::select(., "speciesPair", "Animal_Species", "Plant_Species", "interaction", "pos","neg","tot","prop","Longitude","Latitude")
usable2$Class <- "Frug"

usable_Pol2 <- usable_Pol %>% dplyr::rename(., Animal_Species=Pollinator_Species, Longitude=longitude, Latitude=latitude) %>% dplyr::select(., "speciesPair", "Animal_Species", "Plant_Species", "interaction", "pos","neg","tot","prop","Longitude","Latitude")
usable_Pol2$Class <- "Poll"

dat <- rbind(usable2, usable_Pol2)

#write.csv(dat, file="data/interactionOccs.csv", row.names = F)
#save(WolMeta, Moulatletval, file="data/interactionWebs.RDA")
```

Loading in the outputs created from above
```{r}
dat <- read.csv(file="data/interactionOccs.csv")
load(file="data/interactionWebs.RDA")
```

Grabbing taxonkeys from rgbif to more easily interface with gbifdb
```{r}
taxa <- rgbif::name_backbone_checklist(unique(dat$Animal_Species, dat$Plant_Species))
#Searched term is in verbatim_name column
taxa_safe <- dplyr::filter(taxa, is.na(speciesKey)==F)
write.csv(taxa_safe, file="backbone_matches.csv", row.names=FALSE)
```



Grabbing occurence points
```{r, eval=FALSE}
gbif <- gbif_local(dir='../../../GBIF_local/occurrence/2024-04-01') #Tell R where to find our local GBIF copy
```

# Quantifying interaction specialism
```{r}
FrugPartners <- dplyr::filter(Moulatletval, Frugivore_Species %in% dat$Animal_Species) #All interactions with the focal frugivore species
PollPartners <- dplyr::filter(WolPols, species2 %in% dat$Animal_Species) #All interactions with the focal pollinator species

trait_vector <- c("leaf area", "maximum fruit length", "maximum whole plant height", "maximum whole plant longevity", "minimum fruit length", "plant fruiting duration", "seed length", "seed mass", "whole plant height")

plants <- unique(FrugPartners$Plant_Species, WolPols$species1)
plants <- plants[grepl("\\d", plants)==FALSE]

save(plants, file="BIENstuff.Rda")
```

Query those plants in BIEN
```{r}
plant_traits <- BIEN::BIEN_trait_species(species=plants) #I had trouble running this all at once, so I split the query into 4 files of ~1k-1.5K each  

#write.csv(plant_traits, file="data/traits/plant_traits5K.csv", row.names = F)

BIENSP <- BIEN::BIEN_list_all()

pmatches <- plants[plants %in% BIENSP$species]
```
Loading in those plant traits and taking species-level averages


```{r}
dat1 <- read.csv(file="data/traits/plant_traits1K.csv")
dat2 <- read.csv(file="data/traits/plant_traits2K.csv")
dat34 <- read.csv(file="data/traits/plant_traits3-4K.csv")
dat5 <- read.csv(file="data/traits/plant_traits5K.csv")

ptraits <- rbind(dat1, dat2, dat34, dat5)

psums <- ptraits %>% group_by(., scrubbed_species_binomial, trait_name) %>%  dplyr::summarise(trait_mean=mean(trait_value, na.rm = TRUE))

ptrats_quant <- ptraits %>% dplyr::filter(., is.na(unit)==FALSE)
ptrats_quant$trait_value <- as.numeric(ptrats_quant$trait_value)

ptrats_qual <- ptraits %>% dplyr::filter(., is.na(unit)==TRUE)

ptraitsum <- ptrats_quant %>% group_by(., scrubbed_species_binomial, trait_name) %>%  dplyr::summarise(trait_mean=mean(trait_value, na.rm = TRUE)) %>% dplyr::filter(., trait_mean>0)
```

Let's pivot these traits wider and see which ones we have a bunch of estimates of.
```{r}
wide <- pivot_wider(ptraitsum, id_cols=scrubbed_species_binomial, names_from=trait_name, values_from=trait_mean) #Pivot_wider

#filling in plant height. For species that don't have a "whole plant height" sub with max plant height
wide$`whole plant height`[is.na(wide$`maximum whole plant height`)==F& is.na(wide$`whole plant height`)==T] <- wide$`maximum whole plant height`[is.na(wide$`maximum whole plant height`)==F& is.na(wide$`whole plant height`)==T]

wide$`whole plant height`[is.na(wide$`minimum whole plant height`)== F& is.na(wide$`whole plant height`)==T] <- wide$`maximum whole plant height`[is.na(wide$`maximum whole plant height`)==F& is.na(wide$`whole plant height`)==T]

#Summarising how many species we have trait values for
sort(nrow(wide)-colSums(is.na(wide)), decreasing=T)

#Let's split across our networks and see if it's any better
pollwide <- dplyr::filter(wide, scrubbed_species_binomial %in% WolPols$species1)
sort(nrow(pollwide)-colSums(is.na(pollwide)), decreasing=T)
length(unique(WolPols$species1))


frugwide <- dplyr::filter(wide, scrubbed_species_binomial %in% FrugPartners$Plant_Species)
length(unique(FrugPartners$Plant_Species))
```
Conclusion: We just don't have enough plant trait data, at least not from BIEN alone.

Let's try to add traits from GIFT and TRY

GIFT First
```{r}
trait_meta <- GIFT_traits_meta()
GIFT_query <- dplyr::filter(trait_meta, Trait2 %in% c("Plant_height_mean", "DBH_min", "DBH_max", "Lifespan", "Seed_length_mean", "Fruit_length_mean", "Flower_colour", "Inflorescence", "SLA_mean", "Leaf_size_mean"))

GIFT_Traits <- GIFT_traits(
  trait_IDs = GIFT_query$Lvl3,
  agreement = 0.66,
  bias_ref = TRUE,
  bias_deriv = TRUE,
  api = "https://gift.uni-goettingen.de/api/extended/",
  GIFT_version = "latest"
)

colnames(GIFT_Traits)
head(GIFT_Traits)

GIFT_Traits <- dplyr::filter(GIFT_Traits, work_species %in% plants)
```
So Gift adds some measures and ~156 new species, but all in all not that many. Let's check try


```{r}
focal <- c(unique(dat$Animal_Species), unique(dat$Plant_Species))
```


# Querying GBIF occurence points

We did some querying on another machine; let's see what data we've got
```{r}
toquery <- unique(c(dat$Animal_Species, dat$Plant_Species))
save(toquery, file="GBIFdb_query.RDA")

#tet <- read.csv(file="data/composite_occs.csv")
#tet <- dplyr::filter(tet, species %in% toquery)

#missing <- toquery[toquery %in% tet$species==F]
missing[missing=="Sphaerophoria macrogaster "] <- "Sphaerophoria macrogaster"
#save(missing, file="missingtoQuery.RDA")
```

Quantifying range overlap

```{r}
overlap <- dplyr::select(dat, speciesPair, Animal_Species, Plant_Species) %>% unique()

gsub(" ","_",paste("MaxentModels2/Maxent_test", tolower(dat$Animal_Species[3])))
```


# Creating SDMS

First, make a function to train Maxent
```{r}
trainMaxent <- function(Occ, seed=1, split=0.75, sp="SpeciesName", cropextent=c(-80,-35,-60,5)){
    Occ <- as.data.frame(Occ)
    colnames(Occ) <- c("species", "decimalLongitude", "decimalLatitude")
    Occ['cells']<-terra::cellFromXY(object= Clima[[1]], xy = Occ[,2:3]) #Grab the occurrence cells
    #creating a 200km2 buffer to select the psudo-absence points
    Occ <- unique(Occ) #remove redundant records
    OccSf<-sf::st_as_sf(x=Occ[,2:3], coords = c("decimalLongitude",'decimalLatitude'), 
                        crs=sp::CRS("EPSG:4326")) #crs=sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
    OccBuffer<-sf::st_buffer(OccSf, dist=2) #Create buffer objects with 2deg (~200km) buffers
    OccBuffer<-sf::st_union(OccBuffer) #Merge buffer objects into one
    
    
    ##Masking the buffer so that it does not occur in the ocean
    OccBufferVect <- terra::vect(OccBuffer)
    OccBufferRas <-terra::rasterize(x = OccBufferVect, y=Clima)
    OccBufferRas<-raster::mask(x = OccBufferRas, mask = Clima[[1]])
    
    ##Selecting the potential pseudo absence sites
    AllPseudo <- terra::as.points(OccBufferRas)
    AllPseudo <- raster::extract(x= Clima[[1]], AllPseudo[,1:2],cell=T)
    AllPseudo <-AllPseudo[-(which(AllPseudo$cell%in%Occ$cells)),] #remove true presence from potential psuedo points
    
    #Actually sample psuedoabsences
    set.seed(seed)
    PseudoA<-sample(x = AllPseudo$cell, size = nrow(Occ)) #Sample a number of psuedoA equal to # of occurances
    PseudoA<-as.data.frame(raster::xyFromCell(object = Clima[[1]], cell = PseudoA)) #Make a df
    
    #Now, train a Maxent model
    Occurrences<-cbind(Occ[,2:3], PseudoA[,1:2]) #bind into 4 cols; left is real, right is associated psuedo
    colnames(Occurrences)<-c('Long','Lat','x','y')
    

    id.training<-sample(1:nrow(Occurrences),round(split*nrow(Occurrences),0)) #create test-train split (split=percent train)
    training<-dismo::prepareData(x=raster.comb, p=Occurrences[id.training,c("Long", "Lat")], b=Occurrences[id.training,c("x", "y")])  #Use dismo prepare data to set up df
    testing<-dismo::prepareData(x=raster.comb, p=Occurrences[-id.training,c("Long", "Lat")], b=Occurrences[-id.training,c("x", "y")])    
    training<-na.omit(training)
    testing<-na.omit(testing)
      
    colnames(Occurrences)<-rep(c('Long','Lat'),2) #Change names
    testingPresPA<-rbind.data.frame(Occurrences[-id.training,1:2],Occurrences[-id.training,3:4])
    
          ##Maxent
    Sys.setenv(NOAWT=TRUE)
    Maxent.Model <-dismo::maxent(x = as.data.frame(training[,-1]), p = as.data.frame(training[,1])) #Train Maxent Model
    
    
    Maxent.0  <-dismo::predict(object = Maxent.Model, x = raster.comb, args='outputformat=cloglog') #Predict suitability according to trained model
    Maxent.eval<-evaluate(p = testing[testing[,"pb"]==1,-1], a = testing[testing[,"pb"]==0,-1], model = Maxent.Model)

    
    Max0cut <- Maxent.0
    Max0cut <- terra::crop(x=Max0cut, y=cropextent) #Crop the predicted model to smaller extent
    
    output <- list(prediction=Max0cut, eval=Maxent.eval, sp=sp)
    return(output)
}    
```

Perform a PCA on our environmental data to grab some predictors
```{r}
Clima <- geodata::worldclim_global("worldclim", var="bio", res=2.5)
tet$cells <- terra::cellFromXY(object= Clima[[1]], xy = tet[,5:4])

indcells_tet <- dplyr::group_by(tet, species, cells) %>% dplyr::slice_sample(n = 1)

OccSf <-sf::st_as_sf(x=tet[1:1000,5:4], coords = c("decimalLongitude",'decimalLatitude'), 
                        crs=sp::CRS("EPSG:4326")) #crs=sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

points_proj <- sf::st_transform(OccSf, crs = "+proj=moll")

# Create 200 km buffers (buffer distance in meters)
buffers <- sf::st_buffer(points_proj, dist = 200000)

OccBuffer <-sf::st_union(buffers) #Merge buffer objects into one


plot(Clima[[1]])
polygon(buffers)

points(points_proj, pch=16)


OccSf <-sf::st_as_sf(x=indcells_tet[,5:4], coords = c("decimalLongitude",'decimalLatitude'), 
                        crs=sp::CRS("ESRI:54009")) #Using an equal-distance projection

OccBuffer <-sf::st_buffer(OccSf, dist=2) #Create buffer objects with 2deg (~200km) buffers

plot(OccBuffer)
plot(Clima[[1]])
points(OccSf)
```



